Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-07-23 output/paper/title_page.qmd
Added modified title page.

@@

>>>>

- Type of manuscript: *Original research article*.
- Manuscript title: *Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula*.
- Running head up: *Endocrine Disruptors & Childhood Attention*.
- Corresponding author: Martine Vrijheid, Doctor Aiguader 88 (08003, Barcelona, Spain), martine.vrijheid@isglobal.org, +34 93 2147350 (Ms Iolanda Molina, personal assistant).

@@

## Conflicts of Interest

The authors report no conflicts of interest.

## Data Sharing and Code

Access to HELIX data is based on approval by the HELIX Project Executive Committee and by the individual cohorts. Further details on the content of the data warehouse (data catalog) and procedures for external access are described on the project website (http://www.projecthelix.eu/index.php/es/data-inventory).

The R code to reproduce analyses and results is available online (https://github.com/lorenzoFabbri/paper-helixSC-neuro).
